pirouette: Determining the error BEAST2 makes in inferring a phylogeny

### 2019-03-11 article.tex
Add first half of example 3's pipeline

Although many possible tests can be performed, 
we present here only four \giovanni{five?} example research questions (ERQ) that \verb;pirouette; can answer. 
For these ERQs we will estimate the error made by BEAST2 when 
using a birth-death tree prior, in recovering an original tree 
generated under a Yule generative prior.

@@

  \begin{tabular}{|@{}c|p{4cm}|p{9cm}|p{3cm}@{}|}
    \hline
    \centering
    \textbf{Symbol} & \textbf{Macro-argument} & \textbf{Description} & \textbf{Includes} \\
    \hline
    $\mathit{G}$ & Generative prior & Diversification model to generate the 'true' tree & $\mathit{t_{p}}$ \\
    $\mathit{A}$ & Alignment model & Model used to simulate the alignment ($\mathit{c_{m}}$ must be strict) & $\mathit{c_{m}}, \mathit{s_{m}}, \mathit{m_{r}}, \mathit{r_{s}}$ \\
    $\mathit{I}$ & Inference model & Phylogenetic inference model to run BEAST2 & $\mathit{c_{m}},\mathit{s_{m}},\mathit{t_{p}},\mathit{m_{p}},\mathit{m_{s}}$ \\
    $\mathit{C}$ & Inference conditions & Conditions under which $\mathit{I}$ is used in the inference & $\mathit{m_{t}}, \mathit{r_{i}}$\\
    $\mathit{X}$ & Experiment & Full setting for the BEAST2 run & $\mathit{I},\mathit{C}$ \\
    $\mathit{E}$ & Error measure parameters & Errors measurement setup & $\mathit{e_{f}}$\\
    $\mathit{T}$ & Twinning parameters & Twin tree creation procedure & $\mathit{t_{m}}$\\
    \hline 
  \end{tabular}
  \caption{
    Definitions of terms and relative symbols used in the main text and in Fig~\ref{fig:pipeline}.
  }
  \label{tab:definitions}
  \giovanni{Should we rename "Twinning Parameters" to "Twinning model" and "twin model" to "twin prior"?}
\end{sidewaystable}

@@

>>>>

Although many possible tests can be performed, 
we present here only five example research questions (ERQ) that \verb;pirouette; can answer. 
For these ERQs we will estimate the error made by BEAST2 when 
using a birth-death tree prior, in recovering an original tree 
generated under a Yule generative prior.

@@

  \begin{tabular}{|@{}c|p{4cm}|p{9cm}|p{3cm}@{}|}
    \hline
    \centering
    \textbf{Symbol} & \textbf{Macro-argument} & \textbf{Description} & \textbf{Includes} \\
    \hline
    $\mathit{G}$ & Generative prior & Diversification model to generate the 'true' tree & $\mathit{t_{p}}$ \\
    $\mathit{A}$ & Alignment model & Model used to simulate the alignment ($\mathit{c_{m}}$ must be strict) & $\mathit{c_{m}}, \mathit{s_{m}}, \mathit{m_{r}}, \mathit{r_{s}}$ \\
    $\mathit{I}$ & Inference model & Phylogenetic inference model to run BEAST2 & $\mathit{c_{m}},\mathit{s_{m}},\mathit{t_{p}},\mathit{m_{p}},\mathit{m_{s}}$ \\
    $\mathit{C}$ & Inference conditions & Conditions under which $\mathit{I}$ is used in the inference & $\mathit{m_{t}}, \mathit{r_{i}}$\\
    $\mathit{X}$ & Experiment & Full setting for the BEAST2 run & $\mathit{I},\mathit{C}$ \\
    $\mathit{E}$ & Error measure parameters & Errors measurement setup & $\mathit{e_{f}}$\\
    $\mathit{T}$ & Twinning parameters & Twin tree creation procedure & $\mathit{t_{m}}$\\
    \hline 
  \end{tabular}
  \caption{
    Definitions of terms and relative symbols used in the main text and in Fig~\ref{fig:pipeline}.
  }
  \label{tab:definitions}
  \giovanni{
    Should we rename "Twinning Parameters" to "Twinning model"?
  }
  \richel{
    As the twinning parameters contain more than only the twin model's tree prior,
    I suggest to keep it 'twinning parameters'
  }
  \giovanni{
    Should we rename "twin model" to "twin prior"?
  }
  \richel{
    I think that's a great idea! I would prefer the name 'twin tree prior' even
    better
  }
\end{sidewaystable}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h]
  \centering
  \resizebox {0.8\columnwidth} {!} {
    \begin{tikzpicture}[
      ->,>=stealth',shorten >=1pt,auto,
      node distance=0.25\textheight, 
      semithick
    ]   
    \tikzstyle{every state}=[]
    \node[state, draw=none] (O) [] {
    };   
    \node[state] (A) [right of = O, rectangle] {
      \includegraphics[height=0.2\textheight]{example_3_true_tree.png}
    };   
    \node[state] (B) [below of = A, rectangle] {
      \includegraphics[height=0.2\textheight]{example_3_true_alignment.png}
    };   
    \node[state] (C) [below of = B, rectangle] {
      \includegraphics[height=0.2\textheight]{example_3_true_posterior_gen.png}
    };   
    \node[state] (D) [below of = C, rectangle] {
      \includegraphics[height=0.2\textheight]{example_3_error_violin.png}
    };   
    \path 
      (O) edge [anchor = south] node {} (A)
      (A) edge [anchor = south] node {} (B)
      (B) edge [anchor = south] node {} (C)
      (C) edge [anchor = south] node {} (D)
    ; 
    \end{tikzpicture}
  }
  \label{fig:example_3_full_pipeline}
  \caption{Example 3: full pipeline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
